I could not have made it here without the unwavering support of my advisor Yanbei Chen. He helped me navigate the world of gravitational physics and stuck with me when I explored new topics. More importantly, he was interested in not only my success as a researcher but also my happiness as a person.

I also owe a huge thanks to Rana Adihikari, who inspired new research directions later in my PhD. I would not have been able to finish this thesis without his mentorship and patience. 

I greatly appreciate the guidance that I received from the rest of my committee, Saul Teukolsky, who frequently answered my many questions throughout my degree, and Yaser Abu-Mostafa, who joined my committee even though it was outside of his research interests.

I'm extremely grateful to the prior generation of TAPIR graduate students, especially Huan Yang, Aaron Zimmerman, and my undergraduate advisor Rob Owen. Huan, Aaron, and Rob all invested a significant amount of time and energy in my development as a physicist. 

I'm thankful that I worked with and learned from many brilliant and altruistic people at Caltech, including but not limited to: Chad Galley, Matthew Glieser (a special thanks for the thesis template help), Kevin Barkett, JoAnn Boyd, Craig Cahillane, Boayi Chen, Bassam Helou, Max Isi, Kevin Kuns, Yichu Ma, Morgan Nanez, David Nichols, Masha Okonouva, Belinda Pang, Mark Scheel, Leo Stein, Anandh Swaminathan, Ron Tso, Vija Varma, Hang Yu (a special thanks for helping me learn the background for the noise regression work)

And obviously a huge thanks to my mom, dad, and siblings Ian, Melissa, and Allie, as well as all of my friends.


